Triangulating iconicity: Coding, consistency & calibration

### 2024-04-03 paper_01_consistency.Rmd
knitted md for github

d1 = read_excel("data\\ideophones_coded_MD_original.xlsx") %>% arrange(filename)
d2 = read_excel("data\\ideophones_coded_SP_original.xlsx") %>% arrange(filename)
d2 <- d2[,-c(1:7)] # remove non-unique fields except filename prior to merge

@@

F_consistency$agree <- NA
F_consistency$kappa <- NA
for (i in 1:(length(F_categories)-1)) { # -1 to exclude the notes column
  F_consistency$agree[i] <- (get_agree(data=d.F,cat=F_categories[i]))
  F_consistency$kappa[i] <- (get_kappa(data=d.F,cat=F_categories[i]))
}
F_consistency
mean.na(F_consistency$kappa)

@@

```{r irr_M}
M_consistency$agree <- NA
M_consistency$kappa <- NA
for (i in 1:(length(M_categories)-1)) {
  M_consistency$agree[i] <- (get_agree(data=d.M,cat=M_categories[i]))
  M_consistency$kappa[i] <- (get_kappa(data=d.M,cat=M_categories[i]))
}
M_consistency

@@

The original coding sheet is available as X and the updated coding sheet as X_version_2.

@@

```{r consistency_2ndround}
d1 = read_excel("data\\ideophones_coded_MD.xlsx") %>% arrange(filename)
d2 = read_excel("data\\ideophones_coded_SP.xlsx") %>% arrange(filename)
d2 <- d2[,-c(1:7)] # remove non-unique fields except filename prior to merge

@@

write_xlsx(d.F.inconsistent,path="data\\ideophones_F_consistency_2ndround.xlsx")

@@

d.coded <- read_excel("data\\ideophones_coded_SP.xlsx") %>% 
  arrange(filename) %>%
  dplyr::select(-matches('notes'))
names(d.coded) <- gsub('_SP','',names(d.coded))

@@

# we can have a first look at the basic distribution of guessability by iconicity
d %>%
  group_by(C_cumulative) %>%
  summarise(n=n(),score=mean.na(score))

d %>%
  group_by(C_any1) %>%
  summarise(n=n(),score=mean.na(score))

d %>%
  group_by(C_atleast2) %>%
  summarise(n=n(),score=mean.na(score))

d %>%
  group_by(C_ternary) %>%
  summarise(n=n(),score=mean.na(score))

d %>%
  group_by(C_simple) %>%
  summarise(n=n(),score=mean.na(score))

# finally write this to XLS and CSV
write_xlsx(d,path="data\\ideophones_coded.xlsx")
write.csv(d,file="data\\ideophones_coded.csv")

@@

>>>>

d1 = read_excel("data/ideophones_coded_MD_original.xlsx") %>% arrange(filename)
d2 = read_excel("data/ideophones_coded_SP_original.xlsx") %>% arrange(filename)
d2 <- d2[,-c(1:7)] # remove non-unique fields except filename prior to merge

@@

F_consistency$agree <- NA
F_consistency$kappa <- NA
for (i in 1:(length(F_categories)-1)) { 
  F_consistency$agree[i] <- (get_agree(data=d.F,cat=F_categories[i]))
  F_consistency$kappa[i] <- (get_kappa(data=d.F,cat=F_categories[i]))
}
F_consistency
mean.na(F_consistency$kappa)

@@

```{r irr_M}
M_consistency$agree <- NA
M_consistency$kappa <- NA
for (i in 1:(length(M_categories)-1)) {
  M_consistency$agree[i] <- (get_agree(data=d.M,cat=M_categories[i]))
  M_consistency$kappa[i] <- (get_kappa(data=d.M,cat=M_categories[i]))
}
M_consistency
mean.na(M_consistency$agree)

@@

The original coding sheet is available as `predico_coding_scheme_1.pdf` and the updated coding sheet as `predico_coding_scheme_2.pdf`.

@@

```{r consistency_2ndround}
d1 = read_excel("data/ideophones_coded_MD.xlsx") %>% arrange(filename)
d2 = read_excel("data/ideophones_coded_SP.xlsx") %>% arrange(filename)
d2 <- d2[,-c(1:7)] # remove non-unique fields except filename prior to merge

@@

write_xlsx(d.F.inconsistent,path="data/ideophones_F_consistency_2ndround.xlsx")

@@

d.coded <- read_excel("data/ideophones_coded_SP.xlsx") %>% 
  arrange(filename) %>%
  dplyr::select(-matches('notes'))
names(d.coded) <- gsub('_SP','',names(d.coded))

@@

@@

Finally, we write this to XLSX and CSV files. (Commented out here to avoid overwriting anytime we knit the markdown.)

```{r write_files}

#write_xlsx(d,path="data\\ideophones_coded.xlsx")
#write.csv(d,file="data\\ideophones_coded.csv")
